Semantic information inside sentence embeddings

### 2023-05-10 paper/paper.tex
Added a section about Doc2vec training

\author{Leixin Zhang \\ 
    Computational Linguistics\\
    Seminar für Sprachwissenschaft,
    Universität Tübingen, Germany \\ 
    \texttt{leixin.zhang@student.uni-tuebingen.de}
    }
\author{David Burian\\
  Charles University, Prague\\
  \texttt{david.burian@matfyz.cz}
  }
  % Second Author \\
  % Affiliation / Address line 1 \\
  % Affiliation / Address line 2 \\
  % Affiliation / Address line 3 \\
  % \texttt{email@domain} \\}

@@

% TODO: doc2vec training

>>>>

\author{Leixin Zhang \\ 
    Computational Linguistics\\
    Seminar für Sprachwissenschaft,
    Universität Tübingen, Germany \\ 
    \texttt{leixin.zhang@student.uni-tuebingen.de}
    }
\author{David Burian\\
  Charles University, Prague\\
  \texttt{david.burian@matfyz.cz}
  }
 \author{Vojtěch John\\
 Charles University, Prague\\
 }
  % Second Author \\
  % Affiliation / Address line 1 \\
  % Affiliation / Address line 2 \\
  % Affiliation / Address line 3 \\
  % \texttt{email@domain} \\}

@@

% TODO: doc2vec training - reread
For training the Doc2vec model, we have used the implementation of Doc2vec algorithm
available in the Python package gensim, using a window of size 4 and considering every
word that occured at all (no pruning of rare words) and the vector size of 512.
We have also tried training Doc2Vec models with different embedding sizes (2, 3, 10, 100, 256),
partly so that we could see, ehat impact the size change has on the semantic label predictability, 
partly (especially if we detected a positive correlation between the embedding size and the semantic label
predictability) in order to try and get hint as to how prominent the specific semantic features are 
(i.e. which is the smallest vector size at which given semantic label is predictable from the corresponding embeddings).
